\bf Estimating the number of clusters using Cross Validation

### 2016-02-29 draft2/technometrics.tex
add draft2

\begin{table}[H]
\begin{center}
\captionsetup{justification=centering}
\caption{\label{table2} Number of clusters selected by each algorithm}
\begin{tabular}{lccccc}
    \hline                  
 & Congress Voting && Breast Cancer && Brain Tumours \\ \hline                    
CH-index & $2$ && $2$  && $2$    \\
Hartigan & $3$ && $3$  &&  $4$   \\
Jump & $10$ && $9$ && $1$  \\   
Prediction strength & $2$ &&  $2$ && $1$    \\
Bootstrap stability & $2$ &&  $2$ &&  $7$   \\ 
Gap & $8$ && $10$ && $10$  \\   
Gaussian-Mix & $2$ && $5$ && $2$  \\   
Gabriel & $2$  && $3$  && $5$  \\    
Wold & $2$ && $3$ && $4$ \\  \hline

@@

Since most congressmen vote base on their parties' interest, $2$ parties
(Democratic and Republican) represent two clusters in this data set. So the
optimal number should be two. Close inspection shows $k$-means with
$k=2$ separates the two parties very well with the lowest miss-classification
error $10.43\%$ ($k=3$ has $14.78\%$). Note that CH-index and Bootstrap
stability also return $k=2$, but $2$ is the lower bound those methods can
select for $k$. So it's not clear they actually choose $k=2$ or they hit the
lower bound (they would pick $k=1$ if allowed). For the breast cancer data,
it's known to have at least $2$ cluster based on whether it's benign specimens
or not. But it doesn't mean the optimal $k$ should be $2$.
\cite{fujita2014non} noticed that the malign group is quite heterogeneous and
can be further clustered into at least two subgroups. Hence, the result $k=3$
given by our proposed Gabriel method make sense. For
the brain tumours gene expression data set which is high-dimension, it is also clear that 
the correct number of clusters should be $5$, each cluster corresponding to one type of 
brain tumour. From the table we can see only our proposed
Gabriel method correctly selects $k=5$, underline how
difficult it was to pick the right $k$ when dimension is high.

>>>>

\begin{table}[H]
\begin{center}
\captionsetup{justification=centering}
\caption{\label{table2} Number of clusters selected by each algorithm}
\begin{tabular}{lccccc}
    \hline                  
 & Congress Voting && Breast Cancer && Brain Tumours \\ \hline                    
CH-index & $2$ && $2$  && $2$    \\
Hartigan & $3$ && $3$  &&  $4$   \\
Jump & $10$ && $9$ && $1$  \\   
Prediction strength & $2$ &&  $2$ && $1$    \\
Bootstrap stability & $2$ &&  $2$ &&  $7$   \\ 
Gap & $8$ && $10$ && $10$  \\   
Gaussian-BIC & $2$ && $5$ && $2$  \\   
Gabriel & $2$  && $3$  && $5$  \\    
Gabriel-corr-correct & $2$  && $2$  && $5$  \\  
Wold & $2$ && $3$ && $4$ \\  \hline

@@

Since most congressmen vote based on their parties' interest, two parties
(Democratic and Republican) represent two clusters in this data set. So the
optimal number should be two. Close inspection shows $k$-means with
$k=2$ separates the two parties very well with the lowest miss-classification
error $10.43\%$ ($k=3$ has $14.78\%$). Our proposed Gabriel CV method, along with 
several other algorithms correctly pick $k=2$ for this data set. Note that CH-index and Bootstrap
stability also return $k=2$, but $2$ is the lower bound those methods can
select for $k$. So it's not clear they actually choose $k=2$ or they hit the
lower bound (they would pick $k=1$ if allowed).

For the breast cancer data, it's known to have $2$ clusters based on 
whether it's benign specimens or malignant specimens. Although the proposed Gabriel method
picks $k=3$, its correlation-corrected version correctly picks $k=2$. It shows the necessity 
to correct for the high correlation among data features. However, for this data $k=3$ is also
an acceptable answer, as \cite{fujita2014non} noticed that the malign group is quite heterogeneous and
can be further clustered into at least two subgroups.

The brain tumours gene expression data is a typical high-dimension data with $p > n$. It is clear that 
the correct number of clusters should be $5$, each cluster corresponding to one type of 
brain tumour. From table \ref{table2} we can see only our proposed Gabriel method (as well as its correlation-corrected version) correctly selects $k=5$, underline how difficult it was to pick the right $k$ when dimension is high.
